%-------------------------
% Resume in Latex
% Author : Sachin Kumar (Migrated from moderncv format)
% Based on ATS-friendly template
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{graphicx}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\RequirePackage{tikz}
\RequirePackage{xcolor}
\RequirePackage{fontawesome}
\usepackage{tikz}
\usetikzlibrary{svg.path}

\definecolor{cvblue}{HTML}{0E5484}
\definecolor{black}{HTML}{130810}
\definecolor{darkcolor}{HTML}{0F4539}
\definecolor{cvgreen}{HTML}{3BD80D}
\definecolor{taggreen}{HTML}{00E278}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\colorlet{name}{black}
\colorlet{tagline}{darkcolor}
\colorlet{heading}{darkcolor}
\colorlet{headingrule}{cvblue}
\colorlet{accent}{darkcolor}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\large#1} & \textbf{\small #2} \\
      \textit{\large#3} & \textit{\small #4} \\
      
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand\sbullet[1][.5]{\mathbin{\vcenter{\hbox{\scalebox{#1}{$\bullet$}}}}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
{\Huge \scshape Sachin Kumar} \\ \vspace{6pt}

\small 
+91 9501841073 \,|\, 
\href{mailto:sachinmehtab@gmail.com}{sachinmehtab@gmail.com} \,|\, 
Bengaluru, Karnataka, India \,|\, 
\href{https://linkedin.com/in/sachinkumar6174}{LinkedIn} \,|\, 
\href{https://github.com/sachin6174}{GitHub} \,|\, 
\href{https://leetcode.com/u/sachinkumar6174/}{LeetCode} \,|\, 
\href{https://www.sachinserver.in}{sachinserver.in}
\end{center}

\vspace{-2pt}

%----------SUMMARY----------
\section{SUMMARY}
Mac/iOS Developer with 2.7 years of experience in Swift, SwiftUI, Core Data, and macOS/iOS development. Skilled in Xcode, Cocoa, UIKit, and RESTful API integration with expertise in building secure, scalable, user-friendly enterprise applications. Experienced in App Store deployment and applying MVC, MVVM, and VIPER to deliver maintainable, testable solutions. Currently contributing to enterprise-grade applications as a Software Engineer.

%------WORK EXPERIENCE-------
\section{WORK EXPERIENCE}
    \resumeSubHeadingListStart
        \resumeSubheading{Mac/iOS Developer}{\href{https://www.42gears.com/}{42 Gears Mobility Systems Private Limited}}{July 2023 -- Present}{Bangalore}
        \vspace{2pt}
            \resumeItemListStart
                \resumeItem{\normalsize{Developed app management jobs (PKG, DMG installation/upgrade/uninstall) using command-line tools, shell scripting, XPC communication, and daemonization.}}
                \resumeItem{\normalsize{Implemented Downloading Manager (For File Transfer Job) with resumable downloads, progress tracking, concurrent and serial downloads with worker processes.}}
                \resumeItem{\normalsize{Implemented Geofencing with reverse geocoding, and location-based job execution.}}
                \resumeItem{\normalsize{Built device monitoring (uptime, hardware changes), user management, and remote device actions (reboot, shutdown).}}
                \resumeItem{\normalsize{Implemented Core Data for persistent data storage and management.}}
                \resumeItem{\normalsize{Contributed in code migration from MVVM to VIPER.}}
                \resumeItem{\normalsize{Created analytics collection for device events and app usage with structured data transmission.}}
                \resumeItem{\normalsize{Resolved issues in network extensions, QR enrollment, log encryption, WebView, APNs, and job handling architecture.}}
                \resumeItem{\normalsize{Worked on process daemonization, agent launching, menu bar apps, and packaging (DMG, PKG).}}
                \resumeItem{\normalsize{Implemented Just In Time (JIT) Access for elevated privileges on demand.}}
            \resumeItemListEnd
    \resumeSubHeadingListEnd

%------INTERNSHIP-------
\section{INTERNSHIP}
    \resumeSubHeadingListStart
        \resumeSubheading{Mac/iOS Developer Intern}{\href{https://www.42gears.com/}{42 Gears Mobility Systems Private Limited}}{February 2023 -- June 2023}{Bangalore}
        \vspace{2pt}
            \resumeItemListStart
                \resumeItem{\normalsize{Learned Swift, UIKit, SwiftUI, and asynchronous programming for optimized performance.}}
                \resumeItem{\normalsize{Gained expertise in PKG/DMG creation, signing, notarization, CoreData, UserDefaults, and Keychain.}}
                \resumeItem{\normalsize{Developed skills in macOS scripting, Jira issue tracking, and SonarQube code quality.}}
            \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{PROJECTS}
    \vspace{1pt}
    \resumeSubHeadingListStart
        \resumeProjectHeading
            {\href{https://www.42gears.com/products/mobile-device-management/suremdm-agent-for-macos-past-releases/}{\textbf{\large{\underline{SureMDM Agent for macOS}}}} \hspace{0.1cm} 
            \large{\textit{– Enterprise Device Management Platform}}}{Professional Project}
            \resumeItemListStart
                \resumeItem{\normalsize{Enterprise macOS device management agent with app lifecycle management, security policies, and remote administration}}
            \resumeItemListEnd 
            \vspace{-9pt}

        \resumeProjectHeading
            {\href{https://github.com/sachin6174/NotingDown}{\textbf{\large{\underline{NotingDown}}}} \hspace{0.1cm} 
            \large{\textit{– Built with SwiftUI, Core Data}}}{Personal Project}
            \resumeItemListStart
                \resumeItem{\normalsize{SwiftUI and Core Data note-taking app available on \href{https://apps.apple.com/us/app/notingdown/id123456789}{Apple App Store}}}
            \resumeItemListEnd 
            \vspace{-9pt}

        \resumeProjectHeading
            {\href{https://github.com/sachin6174/Guitar-Utility}{\textbf{\large{\underline{Guitar Utility}}}} \hspace{0.1cm} 
            \large{\textit{– Built with SwiftUI}}}{Personal Project}
            \resumeItemListStart
                \resumeItem{\normalsize{SwiftUI app for guitar tuning and metronome beats available on \href{https://apps.apple.com/us/app/guitar-utility/id6751228342}{Apple App Store}}}
            \resumeItemListEnd 
            \vspace{-9pt}

        \resumeProjectHeading
            {\href{https://github.com/sachin6174/secure-text-chrome-extension}{\textbf{\large{\underline{Secure Text}}}} \hspace{0.1cm} 
            \large{\textit{– Built with JavaScript, Chrome APIs}}}{Personal Project}
            \resumeItemListStart
                \resumeItem{\normalsize{\href{https://chromewebstore.google.com/detail/secure-text/ankgchfieiimiijhlcjcongijapefmei}{Chrome extension} for text encryption/decryption with Base64/Base32 encoding}}
            \resumeItemListEnd 
            \vspace{-9pt}
    \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{SKILLS}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{\normalsize{Languages:}}{ 
     \normalsize{Swift, Objective-C}} \\
     \textbf{\normalsize{Frameworks \& UI:}}{ 
     \normalsize{UIKit, SwiftUI, Xcode}} \\
     \textbf{\normalsize{Data \& Storage:}}{ \normalsize{CoreData, SQL, MongoDB}} \\
     \textbf{\normalsize{Testing \& Patterns: }}{ \normalsize{XCTest, XCUITest, MVC/MVVM/VIPER, Debugging}} \\
     \textbf{\normalsize{Concurrency \& Web: }}{\normalsize{Swift Concurrency, React, Node}} \\
     \textbf{\normalsize{Tools \& Platforms: }}{\normalsize{Git/GitHub/GitLab/JIRA, Data Structures, Algorithms}} \\
     \textbf{\normalsize{AI Tools: }}{\normalsize{AI - Copilot, ClaudeCode, ChatGPT}} \\
    }}
 \end{itemize}

%-----------EDUCATION-----------
\section{EDUCATION}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Chandigarh Group of Colleges}{August 2019 - May 2023}
      {Bachelor of Engineering in Computer Science, CGPA: \textbf{7.9}}{Landran, Mohali}
  \resumeSubHeadingListEnd

%-----------CERTIFICATIONS-----------
\section{CERTIFICATIONS}
    \vspace{0pt}
    \resumeItemListStart
        \resumeItem{\normalsize{\href{http://ninjasfiles.s3.amazonaws.com/certificate18894980e4209379ac28665887f78da42bac5c2.pdf}{\textbf{System Design}}: Coding Ninjas (November 2021 - February 2022)}}
        \resumeItem{\normalsize{\href{https://ninjasfiles.s3.amazonaws.com/certificate19853580c201378561a01f48ae87f59e9220db2.pdf}{\textbf{Data Structures in C++}}: Coding Ninjas (January 2022 - April 2022)}}
    \resumeItemListEnd

%-----------ACHIEVEMENTS-----------
\section{ACHIEVEMENTS}
    \vspace{0pt}
    \resumeItemListStart
        \resumeItem{\normalsize{\href{https://github.com/abhikumar002/Agentic-Gig-Project}{\textbf{Google Cloud Agentic AI Hackathon 2025}}: Selected among top 700 teams from 57,000+ developers. Built an AI-powered platform providing farmers expert advice using Next.js, Firebase, Python, and Kotlin.}}
    \resumeItemListEnd

%-----------HOBBIES---------------
\section{INTERESTS}
    \vspace{0pt}
    \resumeItemListStart
        \resumeItem{\normalsize{Exploring AI tools, Reading Literature, Drawing, Listening to Music}}
    \resumeItemListEnd

\end{document}