%%%%%%%%%%%%%%%%%
% This is a two-column CV template based on moderncv.cls
% Adapted for Sachin Kumar's resume
%%%%%%%%%%%%%%%%%

% environment
\documentclass[10pt,a4paper]{moderncv}
\moderncvtheme[blue]{banking}
\nopagenumbers{}

\usepackage[T1]{fontenc}
\usepackage{inputenc}
\usepackage[scale=0.9]{geometry}
\usepackage{tabularx}
\usepackage{mathpazo}

% macro
\renewcommand*{\labelitemi}{-}

% Make all hyperlinks underlined
\let\oldhref\href
\renewcommand{\href}[2]{\oldhref{#1}{\underline{#2}}}

\newcolumntype{L}{>{\raggedright\arraybackslash}X}
\newcolumntype{C}{>{\centering\arraybackslash}X}
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}

\newcommand*{\experienceentry}[5][1.5mm]{
    \begin{tabularx}{\textwidth}{L}
        {\bfseries\large #2}
    \end{tabularx}
    \vspace{1mm}
    \begin{tabularx}{\textwidth}{L}
        {\bfseries #3}
    \end{tabularx}
    \vspace{1mm}
    \begin{tabularx}{\textwidth}{L}
        {\faCalendar\enspace #4 \faMapMarker\enspace #5}
    \end{tabularx}
    \par\addvspace{#1}
}

\newcommand*{\educationentry}[4][0.5mm]{
    \begin{tabularx}{\textwidth}{LR}
        {\bfseries #3} & {\bfseries #4} \\
    \end{tabularx}
    {\itshape #2}
    \par\addvspace{#1}
}

\newcommand*{\scoreentry}[3][2.5mm]{
    {\bfseries #2} \\
    {\itshape #3}
    \par\addvspace{#1}
}

% preamble
\firstname{Sachin}
\familyname{Kumar}
\address{Bangalore, India}{}

% document
\begin{document}
\maketitle
\vspace{-9.0mm}
\begin{tabularx}{\textwidth}{C C C C}
    \emailsymbol\enspace \emaillink{sachinmehtab@gmail.com} & \mobilephonesymbol\enspace +91 9501841073 & \faLinkedin\enspace \href{https://linkedin.com/in/sachinkumar6174}{sachinkumar6174*} & \faGithub\enspace \href{https://github.com/sachin6174}{sachin6174*}
\end{tabularx}
\vspace{-2.0mm}

% left column
\begin{minipage}[t]{0.60\textwidth}
\section{PROFESSIONAL EXPERIENCE}
\experienceentry{Mac/iOS Developer}{\href{https://www.42gears.com/}{42 Gears Mobility Systems Private Limited*}}{July 2023 - Current}{Bangalore}

\begin{itemize}
    \item Developed app management jobs (PKG, DMG installation/upgrade/uninstall) using command-line tools, shell scripting, XPC communication, and daemonization.
    \item Implemented Downloading Manager (For File Transfer Job) with resumable downloads, progress tracking, concurrent and serial downloads with worker processes.
    \item Implemented Geofencing with reverse geocoding, and location-based job execution.
    \item Built device monitoring (uptime, hardware changes), user management, and remote device actions (reboot, shutdown).
    \item Implemented Core Data for persistent data storage and management.
    \item Contributed in code migration from MVVM to VIPER.
    \item Created analytics collection for device events and app usage with structured data transmission.
    \item Resolved issues in network extensions, QR enrollment, log encryption, WebView, APNs, and job handling architecture.
    \item Worked on process daemonization, agent launching, menu bar apps, and packaging (DMG, PKG).
    \item Implemented Just In Time (JIT) Access for elevated privileges on demand.
\end{itemize}
\vspace{2.0mm}

% Dashed line separator
\noindent\makebox[\linewidth]{\dotfill}
\vspace{2.0mm}

\experienceentry{Mac/iOS Developer Intern}{\href{https://www.42gears.com/}{42 Gears Mobility Systems Private Limited*}}{February 2023 - June 2023}{Bangalore}

\begin{itemize}
    \item Learned Swift, UIKit, SwiftUI, and asynchronous programming for optimized performance.
    \item Gained expertise in PKG/DMG creation, signing, notarization, CoreData, UserDefaults, and Keychain.
    \item Developed skills in macOS scripting, Jira issue tracking, and SonarQube code quality.
\end{itemize}

\section{PROJECTS}
\subsection{\href{https://www.42gears.com/products/mobile-device-management/suremdm-agent-for-macos-past-releases/}{SureMDM Agent for macOS*}}
\begin{itemize}
    \item Enterprise macOS device management agent with app lifecycle management, security policies, and remote administration
\end{itemize}

\subsection{\href{https://github.com/sachin6174/NotingDown}{NotingDown*}}
\begin{itemize}
    \item SwiftUI and Core Data note-taking app on \href{https://apps.apple.com/us/app/notingdown/id123456789}{Apple App Store*}
\end{itemize}

\subsection{\href{https://github.com/sachin6174/secure-text-chrome-extension}{Secure Text*}}
\begin{itemize}
    \item \href{https://chromewebstore.google.com/detail/secure-text/ankgchfieiimiijhlcjcongijapefmei}{Chrome extension*} for text encryption/decryption with Base64/Base32 encoding
\end{itemize}

\subsection{\href{https://github.com/sachin6174/Guitar-Utility}{Guitar Utility*}}
\begin{itemize}
    \item SwiftUI app for guitar tuning and metronome beats (App Store review process)
\end{itemize}

\end{minipage}
\hfill
% right column
\begin{minipage}[t]{0.35\textwidth}
\section{SUMMARY}
Mac/iOS Developer with 2.7 years experience in SureMDM agent development for macOS device management. Skilled in Swift , SwiftUI ,Core Data , command line tools and macOS application development.

\section{ACHIEVEMENTS}
\textbf{\href{https://github.com/abhikumar002/Agentic-Gig-Project}{Google Cloud Agentic AI Hackathon 2025*}} \\
Selected among top 700 teams from 57,000+ developers. Built an AI-powered platform providing farmers expert advice using Next.js, Firebase, Python, and Kotlin.

\section{SKILLS}
\begin{tabularx}{\textwidth}{XX}
\textbf{Swift} & \textbf{Objective-C} \\
\textbf{UIKit} & \textbf{SwiftUI} \\
\textbf{Xcode} & \textbf{CoreData} \\
\textbf{Debugging} & \textbf{MVC/MVVM/VIPER} \\
\textbf{Swift Concurrency} & \textbf{XCTest} \\
\textbf{XCUITest} & \textbf{React} \\
\textbf{Node} & \textbf{SQL} \\
\textbf{MongoDB} & \textbf{Git/GitHub/GitLab/JIRA} \\
\textbf{Data Structures} & \textbf{Algorithums} \\
\textbf{AI - Copilot} & \textbf{ClaudeCode,ChatGPT} \\
\end{tabularx}

\section{CONTACT}
\begin{itemize}
    \item Website: \href{https://www.sachinserver.in}{sachinserver.in*}
    \item Phone: +91 9501841073
    \item Email: sachinmehtab@gmail.com
\end{itemize}

\section{PROFILES}
\begin{itemize}
    \item LeetCode: \href{https://leetcode.com/u/sachinkumar6174/}{sachinkumar6174*}
    \item Portfolio: \href{https://sachinserver.in/}{sachinserver.in*}
\end{itemize}

\section{EDUCATION}
B.Tech - Computer Science (2019-2023) \\
\textbf{Chandigarh Group of Colleges} \\
\faCalendar\enspace CGPA: 7.9

\section{HOBBIES}
\begin{itemize}
    \item Exploring AI tools
    \item Reading Literature
    \item Drawing
    \item Listening to Music
\end{itemize}

\end{minipage}

\end{document}